%------------------------------------
% Dario Taraborelli
% Typesetting your academic CV in LaTeX
%
% URL: http://nitens.org/taraborelli/cvtex
% DISCLAIMER: This template is provided for free and without any guarantee
% that it will correctly compile on your system if you have a non-standard
% configuration.
% Some rights reserved: http://creativecommons.org/licenses/by-sa/3.0/
%------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt, a4paper]{article}
\usepackage{fontspec}
\usepackage{enumitem}

% DOCUMENT LAYOUT
\usepackage{geometry}
\geometry{a4paper, textwidth=6in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in, top=.5in, bottom=.35in}
\setlength\parindent{0in}
\pagenumbering{gobble}

% FONTS
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
%\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O}
%\setmonofont[Scale=0.8]{Monaco}
%%% modified by Karol Kozioł for ShareLaTeX use
\setmainfont[
  Ligatures={Common}, Numbers={OldStyle}, Variant=01,
  BoldFont=LinLibertine_RB.otf,
  ItalicFont=LinLibertine_RI.otf,
  BoldItalicFont=LinLibertine_RBI.otf
]{LinLibertine_R.otf}
\setmonofont[Scale=0.8]{DejaVuSansMono.ttf}

% ---- CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}
% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\setlist[itemize]{topsep=0.55em}
\reversemarginpar

% HEADINGS
\usepackage{sectsty}
\usepackage[normalem]{ulem}
\sectionfont{\mdseries\upshape\Large}
\subsectionfont{\mdseries\scshape\normalsize}
\subsubsectionfont{\mdseries\upshape\large}

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[%dvipdfm,
  bookmarks, colorlinks, breaklinks,
  % ---- FILL IN HERE THE TITLE AND AUTHOR
  pdftitle={Qais Patankar - CV},
  pdfauthor={Qais Patankar},
  pdfproducer={http://nitens.org/taraborelli/cvtex}
]{hyperref}
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue}


% DOCUMENT
\begin{document}
{\huge Qais Patankar}
\hspace{0.5em}
\href{mailto:me@qaisjp.com}{me@qaisjp.com} |
\href{https://qaisjp.com}{qaisjp.com}
\hfill qaisjp on \href{https://github.com/qaisjp}{GitHub}
\& \href{https://uk.linkedin.com/in/qaisjp}{LinkedIn}\\

%%%%%%%%%
\hrule

% \vspace{-0.5em}
\section*{Work \& Experience}
\vspace{-0.5em}
% \noindent

\years{June 2020 -\\ present}
Software Engineer, Stripe - \emph{Dublin, Ireland}
\hfill \href{https://stripe.com}{stripe.com}
\begin{itemize}
  \itemsep0em
  \item \emph{Technologies: Ruby, Bazel, Go}
  \item Developer Productivity and Test Infrastructure—enabling Stripe to operate with urgency, focus and safety by improving the reliability, availability and efficiency of our core CI infrastructure.
\end{itemize}

\years{Aug 2019 -\\ Jan 2020}
Freelance Software Engineer, Blue Wheel Media - \emph{Remote, Edinburgh, UK}
\hfill \href{https://bluewheelmedia.com/}{bluewheelmedia.com}
\begin{itemize}
  \itemsep0em
  \item Developing a scalable ad campaign manager in Go. \emph{Technologies: Go, GraphQL, Protocol Buffers}
  \item Simplified development by building a multi-account Amazon Advertising gateway API microservice.
  \item Created filtering system that supports an assortment of conjunctions, disjunctions and operators.
\end{itemize}

\years{July 2019 -\\ Aug 2019} Software Engineering Intern, HENNGE - \emph{Tokyo, Japan}
\hfill \href{https://hennge.com/global/}{hennge.com}
\begin{itemize}
  \itemsep0em
  \item Deployed an inventory management interface to production. \emph{Technologies: Go, React, PostgreSQL}
  \item Improved security \& access management by integrating SAML authorization and authentication.
  \item Sped up development time and deployments by refactoring DB \& introducing a migration system.
\end{itemize}

\years{Jun 2018 -\\ Aug 2018} MyEd Development Intern, Information Services, University of Edinburgh \hfill \href{http://www.myed.ed.ac.uk/}{www.myed.ed.ac.uk}
\begin{itemize}
  \itemsep0em
  \item Improved university portal for \textbf{590,000+} users by developing new React components.
  \item Sped up developer onboarding by creating and documenting a Docker environment.
  \item Optimised UX designer workflow by automating processes, and supporting card-sorting sessions.
\end{itemize}

\years{2016 - 2020 \\\\President\\2017 - 2018} President, Technology Society, University of Edinburgh \hfill \href{https://comp-soc.com/}{comp-soc.com}

% \vspace{-1em}
\begin{itemize}
  \itemsep0em
  \item \emph{Technologies: Python, Django, Docker, JavaScript, Go, Stripe}
  \item As President, managed a \textbf{£30,000} budget (sponsors incl. Google, Microsoft, Amazon, JP Morgan).
  \item Processed \textbf{£15,500+} in payments by creating secure ticketing systems \& a \href{https://web.archive.org/web/20180220170809/https://comp-soc.com/hoodies-old}{hoodie customisation site}.
  \item Doubled size to \textbf{200} people as Director. Built website and application platform for \textbf{three} hackathons.
  \item Held \textbf{three} roles across \textbf{four} years. Currently elected to represent all undergrads for a second term.
\end{itemize}


% \years{Jan 2017 -\\ present} Systems Administrator, Tardis Project, University of Edinburgh
% \hfill \href{http://wiki.tardis.ed.ac.uk}{wiki.tardis.ed.ac.uk}\\
% \emph{Maintain and set up containers and virtual machines for various services used by roughly \textbf{770} users}. \\

% \years{Sept 2017 -\\ present}
% Teaching Support Provider, School of Informatics, University of Edinburgh
% \hfill \href{http://www.inf.ed.ac.uk/}{www.inf.ed.ac.uk}\\
% \emph{Teach Introduction to Haskell, Intro to Linux, and Intro to Java to a cohort of \textbf{over 300} students}.\\

\years{July 2014 -\\ Nov 2014} Gameplay \& UI Programmer, Those Awesome Guys - \emph{Remote, Leeds, UK}
\hfill \href{http://www.moveordiegame.com/}{moveordiegame.com}
\begin{itemize}
  \itemsep0em
  \item Developed multiplayer game "Move or Die", \textbf{1m+ owners}. \emph{Technologies: Lua, Love2D}
  \item Introduced Git VCS as first external developer \& trained developers on how to use Git effectively.
  \item Created configuration system that can read and rewrite a Lua config file whilst retaining comments.
  \item Modularised menu system, built character selection screen, and video settings dynamic preset system.
\end{itemize}

\vspace{-1.5em}
\section*{Open Source}
\vspace{-0.25em}

\years{Oct 2010 -\\ present} Multi Theft Auto
\hfill \href{https://MultiTheftAuto.com}{multitheftauto.com}
% \vspace{-0.5em}
\begin{itemize}
  \itemsep0em
  \item \emph{Technologies: C++, C, Assembly, Reverse Engineering, Lua, Go, TypeScript, Nginx, PHP}
  \item Multiplayer game enjoyed by \textbf{600,000+} users per month \&
        \textbf{300,000+} per week unique users.
  \item Migrated repository to GitHub from Google Code. Currently developing a plugin sharing platform.
  \item Introduced OOP-style Lua interface, added macOS server support, and improved code quality.
  \item Responsible for \textbf{two} most recent releases, including development \& product management.
\end{itemize}

\years{May 2017 -\\ present} matterbridge and go-discord-irc
  \hfill \href{https://github.com/42wim/matterbridge}{matterbridge}, \href{https://github.com/qaisjp/go-discord-irc}{go-discord-irc}
  \begin{itemize}
    \itemsep 0em
    \item go-discord-irc is a bridge I built that connects IRC and Discord.
          matterbridge is a project I contribute to that connects several different chat platforms together.
          \emph{Technologies: Go}
  \end{itemize}

\years{2016 -\\ 2020} Better Informatics \& The Marauder's App
\hfill \href{https://betterinformatics.com}{betterinformatics.com}
\begin{itemize}
  \itemsep0em
  \item \emph{Technologies: Go, Jekyll, JavaScript, Python, Flask, Kerberos, LDAP, SSH, REST API}
\item Scaled \textbf{10x} to over \textbf{1700} students by rebuilding course collaboration \& machine availability webapp.
\item Integrated university’s SSO system (CoSign) by building a Go library and a web API
      \href{https://github.com/qaisjp/gosign}{"gosign"}.
\end{itemize}

%%%%%%%%%
\vspace{-1.5em}
\section*{Awards}
\vspace{-0.5em}

\years{Nov 2019}
  \emph{1st Place, Challenge "Ericsson - Greener City Transport with 5G"},
  \href{https://github.com/qaisjp/league-of-agents}{League of Agents}
  \hfill Junction 2019

  \years{Mar 2019}
  \emph{2nd Place Overall},
  \href{https://devpost.com/software/receipt2fitbit}{Shake It Off!}
  \hfill HackCambridge 4D

\years{Mar 2018}
  \emph{1st Place Overall},
  \href{https://devpost.com/software/shapeshifter-invasion-a-collaborative-turn-based-game-szwkqj}
    {Shapeshifter Invasion}
  \hfill StudentHack 2018

\years{Nov 2017}
  \emph{1st Place for Equal Measures 2030},
  Data Visualisation \hfill JP Morgan Code For Good

\years{Mar 2017}
  \emph{1st Place Game Track},
  \href{https://devpost.com/software/project-minos}{Project Minos}
  \hfill StudentHack 2017

\years{2016 - 2020}
  \emph{Undergraduate Scholarship Recipient}
  \hfill Deutsche Post DHL

%%%%%%%%%%%%%%%%%%%
\vspace{-0.5em}
\section*{Education}
\vspace{-0.5em}

\years{2016 - 2020} BEng (Hons) Computer Science, University of Edinburgh
  --- \emph{First Class Honours}

\vspace{-0.5em}
\begin{itemize}
  \item Coursework: Security 99.5\%,
                    Compilers 99.4\%,
                    Testing 88\% (A),
                    Operating Systems 88\% (A)
\end{itemize}


% \vspace{1cm}
\vfill{}
%\hrulefill

\begin{center}
  {
    \scriptsize  Last updated \today{}
     -- References available by request
     -- Latest version at qais.jp/cv
  }
\end{center}

\end{document}
